\LARGE \bf Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation of RGB-D Images

### 2013-09-13 paper.tex
fix plots, add teaser
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4372 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

Our approach starts with a random forest, providing a noisy local estimate
of semantic classes based on color and depth information. These estimates
are grouped together using a superpixel approach, for which we extend previous
superpixel algorithms from the RGB to the RGB-D domain.
We then build a geometric model of the scene, based on the neighborhood graph
of superpixels.  We use this graph not only to capture spatial relations in the
2D plane of the image, but also to model object distances and surface angles in
3D, using a point cloud generated from the RGB-D image.

@@

@@

\section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}
We take a conditional random field approach, whose nodes represent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding adjacence between superpixels.

@@

\subsection{Low Level Segmentation}
We take a super-pixel based approach to semantic segmentation.
Our superpixel generation is based on the SLIC algorithm~\citep{achanta2012slic}. We extend the
standard SLIC algorithm, which works on the Lab space, to also include 
depth information. The resulting algorithm is a localized $k$-Means in Lab-D-XY space.
Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
RGB segmentation when using additional depth information. On the other hand,
estimation of per-superpixel features based on the 3D point cloud was more
robust when including depth information into the superpixel procedure.
%TODO visualize?
The resulting superpixels are compact in the 2D image. As the corresponding point
cloud is very sparse at depth jumps, it is unfortunately not possible to create
superpixels that are compact in 3D while maintaining a meaningful minimum size.

@@

>>>>

Our approach starts with a random forest, providing a noisy local estimate
of semantic classes based on color and depth information. These estimates
are grouped together using a superpixel approach, for which we extend previous
superpixel algorithms from the RGB to the RGB-D domain.
We then build a geometric model of the scene, based on the neighborhood graph
of superpixels.  We use this graph not only to capture spatial relations in the
2D plane of the image, but also to model object distances and surface angles in
3D, using a point cloud generated from the RGB-D image. The process is depicted
in \Figref{teaser}.

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{images/teaser}
    \end{center}
    \caption{%
        Visualization of the method proposed in this paper see \Secref{learning} for details.\label{teaser}
    \figlabel{height}}
\end{figure}

@@

\section{LEARNING DEPTH-SENSITVE CONDITIONAL RANDOM FIELDS}\seclabel{learning}
We take a conditional random field approach, whose nodes represent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding adjacence between superpixels.

@@

@@

\subsection{Low Level Segmentation}
We take a super-pixel based approach to semantic segmentation.
Our superpixel generation is based on the SLIC algorithm~\citep{achanta2012slic}. We extend the
standard SLIC algorithm, which works on the Lab space, to also include 
depth information. The resulting algorithm is a localized $k$-Means in Lab-D-XY space.
Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
RGB segmentation when using additional depth information. On the other hand,
estimation of per-superpixel features based on the 3D point cloud was more
robust when including depth information into the superpixel procedure.
%TODO visualize?
The resulting superpixels are compact in the 2D image. As the density of the
corresponding point cloud is dependent on the depth, we did not succeed in
creating superpixels that are compact in 3D while maintaining a meaningful
minimum size.
